Getting mortality from atlantisom: backing out F and M from Z

### 2020-01-14 TestCalcFandM.Rmd
added NOBA cod, M still really high, start on numbers based F not done

Is there a mismatch between biomass based F and numbers based Z?

@@

Or maybe spring spawning herring leave the model area and I'm not accounting for that (is this a run with broken migration?).

@@

# align nums previous timestep with catch current timestep

@@

>>>>

Is there a mismatch between biomass based F and numbers based Z? We can't do this comparison for CCA because our catch numbers from the .nc file have the pre-December 2015 bug.

Also, this may indicate that we need to redo calc_Z as cohort-specific after all.

@@

Or maybe spring spawning herring leave the model area and I'm not accounting for that (is this a run with broken migration?). No evidence that these species migrate in documentation.

@@

# work in progress 
# align nums at agecl previous timestep with catch current timestep
# for each agecl: time-1 catch_numsss$atoutput / time totnumss$atoutput
catch_numsss <- catch_numsss %>%
  select(species, agecl, catchtime=time, catchnum=atoutput) %>%
  mutate(Ftime = catchtime - 1)

totnumss <- totnumss %>%
  select(species, agecl, time, popnum=atoutput) %>%
  mutate(Ftime = time)

#not done yet dont use this
timestepnumF <- merge(totnumss, catch_numsss) %>%
  mutate(stepnF = (catchnum/popnum)) %>%
  arrange(Ftime, agecl)

@@

Try this for cod, herring don't have much F

```{r NOBAcod}

species_ss <- "North_atl_cod"

Now estimate cod F from biomass and compare:

```{r NOBAcodFest}

# catch from txt output
truecatchbio <- load_catch(d.name, file_catch = catch.file, fgs = funct.groups)

```{r NOBAcodF_estplot}

Cod F based on biomass isn't that different from the F reported in mort.txt.

Cod M if we believe our Z estimate from calc_Z:

```{r NOBAcodannZ2}

# annM1 <- merge(annZ1, annbioF, all.x = T) %>%
#   mutate(M = Z-annbioF)

plotM <- ggplot() +
  geom_line(data=Zish, aes(x=Time/365, y=relZ, color="mort.txt Z")) +
  geom_line(data=Zish, aes(x=Time/365, y=relM, color="mort.txt M")) +
  #geom_point(data=annM1, aes(x=Time/365, y=M, color="M = endyr Z-F")) +
  geom_point(data=annM2, aes(x=yr, y=M, color="M = sum timestep Z-F")) +
  theme_tufte() +
  theme(legend.position = "bottom", legend.box = "horizontal") +
  scale_color_discrete(NULL) +
  guides(color = guide_legend(nrow = 1)) +
  labs(subtitle = paste(scenario.name, species_ss))

plotM + ylim(0, 10.0)
